Exploring Hillary Clinton's Emails\thanks{STATS 601 final project.}

### 2016-04-18 paper/paper.tex
Adjusting colors.
Minor adjustments.
Minor changes.

\newcommand*{\colsquare}[3][-3.5pt]{\tikz[baseline=-0.5ex]\draw[#2, fill=#2] (0,#1) rectangle ++(#3,#3);}%
\definecolor{cmeet}{HTML}{E31A1C}
\definecolor{cmideast}{HTML}{1F78B4}
\definecolor{cstaff}{HTML}{A6CEE3}
\definecolor{cpolitics}{HTML}{33A02C}
\definecolor{cterror}{HTML}{B2DF8A}
\definecolor{cforeign}{HTML}{FB9A99}
\definecolor{cpress}{HTML}{FF7F00}
\definecolor{chill}{HTML}{6A3D9A}
\definecolor{ccommu}{HTML}{CAB2D6}
\definecolor{ccomm}{HTML}{FDBF6F}

@@

\begin{figure}[htb] \centering
  \begin{subfigure}[t]{.49\linewidth}
    \includegraphics[width=\linewidth]{../images/mds_2d.png}
    \caption{2 Dimensions} \label{fig:mds:2d}
  \end{subfigure}
  \begin{subfigure}[t]{.49\linewidth}
    \includegraphics[width=\linewidth]{../images/mds_3d_1.png}
    \caption{3 Dimensions} \label{fig:mds:3d}
  \end{subfigure}
  \caption{Visualization of a 8,000 email subset using classical multi-dimensional scaling. The distance metric used is cosine distance as defined in Equation~\ref{eq:cos_dist}.}
  \label{fig:mds}
\end{figure}

\begin{figure}[htbp] \centering
  \begin{subfigure}[t]{.7\linewidth}
    \includegraphics[width=\linewidth]{../images/mds_2d_cluster.png}
    \caption{2 Dimensions} \label{fig:cluster:2d}
  \end{subfigure}
  \begin{subfigure}[t]{.7\linewidth}
    \includegraphics[width=\linewidth]{../images/mds_3d_cluster_1.png}
    \caption{3 Dimensions} \label{fig:cluster:3d}
  \end{subfigure}
  \caption{Visualization of the same 8,000 email subset with coloring according to the results from spectral clustering.}
  \label{fig:cluster}
\end{figure}

@@

\begin{table}[htb] \centering
\begin{tabular}{rcl}
  \toprule
  \colsquare{cterror}{10pt} & Terrorism & 5, 22 \\
  \colsquare{cmideast}{10pt} & Middle East & 6, 18, 19, 27, 29 \\
  \colsquare{cforeign}{10pt} & Foreign Policy & 2, 7, 13, 21, 23, 26 \\
  \colsquare{cpolitics}{10pt} & Politics & 11, 17, 25 \\
  \colsquare{cstaff}{10pt} & Staff & 16, 20 \\
  \colsquare{cpress}{10pt} & Press & 4 \\
  \colsquare{chill}{10pt} & Hillary & 12 \\
  \colsquare{cmeet}{10pt} & Meetings & 9, 10, 24, 28, 30 \\
  \colsquare{ccommu}{10pt} & Communication & 1 \\
  \colsquare{ccomm}{10pt} & Common & 3, 8, 14, 15 \\
  \bottomrule
\end{tabular}
\caption{Topic Categorization}
\label{tab:topic_cat}
\end{table}

\begin{table}[htb] \centering
\setlength{\tabcolsep}{1pt}
\begin{tabular}{ccccccccccccccccccccccccc}
  \toprule
  \colsquare[-3pt]{cforeign}{16pt} &
  \colsquare[-3pt]{cmeet}{16pt} &
  \colsquare[-3pt]{cmeet}{16pt} &
  \colsquare[-3pt]{cmeet}{16pt} &
  \colsquare[-3pt]{cmeet}{16pt} &
  \colsquare[-3pt]{cpress}{16pt} &
  \colsquare[-3pt]{cmeet}{16pt} &
  \colsquare[-3pt]{cmideast}{16pt} &
  \colsquare[-3pt]{cmideast}{16pt} &
  \colsquare[-3pt]{cstaff}{16pt} &
  \colsquare[-3pt]{cstaff}{16pt} &
  \colsquare[-3pt]{chill}{16pt} &
  \colsquare[-3pt]{cforeign}{16pt} &
  \colsquare[-3pt]{cpolitics}{16pt} &
  \colsquare[-3pt]{cmideast}{16pt} &
  \colsquare[-3pt]{cmideast}{16pt} &
  \colsquare[-3pt]{cforeign}{16pt} &
  \colsquare[-3pt]{cmideast}{16pt} &
  \colsquare[-3pt]{cterror}{16pt} &
  \colsquare[-3pt]{cforeign}{16pt} &
  \colsquare[-3pt]{cpolitics}{16pt} &
  \colsquare[-3pt]{cforeign}{16pt} &
  \colsquare[-3pt]{cforeign}{16pt} &
  \colsquare[-3pt]{cpolitics}{16pt} &
  \colsquare[-3pt]{cterror}{16pt} \\
  21 & 28 & 30 & 9 & 10 & 4 & 24 & 29 & 18 & 20 & 16 & 12 &
  13 & 17 & 19 & 27 & 23 & 6 & 22 & 2 & 25 & 26 & 7 & 11 & 5 \\
  \bottomrule
\end{tabular}
\setlength{\tabcolsep}{6pt}
\caption{Primary Topic Frequency}
\label{tab:topic_freq}
\end{table}

@@

>>>>

\newcommand*{\colsquare}[3][-3.5pt]{\tikz[baseline=-0.5ex]\draw[#2, fill=#2] (0,#1) rectangle ++(#3,#3);}%
\definecolor{cmeet}{HTML}{B2DF8A}
\definecolor{cmideast}{HTML}{FDBF6F}
\definecolor{cstaff}{HTML}{A6CEE3}
\definecolor{cpolitics}{HTML}{33A02C}
\definecolor{cterror}{HTML}{E31A1C}
\definecolor{cforeign}{HTML}{FF7F00}
\definecolor{cpress}{HTML}{FB9A99}
\definecolor{chill}{HTML}{6A3D9A}
\definecolor{ccomm}{HTML}{1F78B4}

@@

\begin{figure}[htbp] \centering
  \begin{subfigure}[t]{.7\linewidth}
    \includegraphics[width=\linewidth]{../images/mds_2d_cluster.png}
    \caption{2 Dimensions} \label{fig:cluster:2d}
  \end{subfigure}
  \begin{subfigure}[t]{.7\linewidth}
    \includegraphics[width=\linewidth]{../images/mds_3d_cluster_1.png}
    \caption{3 Dimensions} \label{fig:cluster:3d}
  \end{subfigure}
  \caption{Visualization of a 8,000 email subset using classical multi-dimensional scaling and with coloring according to the results from spectral clustering. The similarity and distance metrics used for spectral clustering and MDS, respectively, are cosine similarity and distance as defined in Equations~\ref{eq:cos_sim} and~\ref{eq:cos_dist}.}
  \label{fig:cluster}
\end{figure}

@@

\begin{table}[htb] \centering
\begin{tabular}{rcl}
  \toprule
  \colsquare{cterror}{10pt} & Terrorism & 5, 22 \\
  \colsquare{cmideast}{10pt} & Middle East & 6, 18, 19, 27, 29 \\
  \colsquare{cforeign}{10pt} & Foreign Policy & 2, 7, 13, 21, 23, 26 \\
  \colsquare{cpolitics}{10pt} & Politics & 11, 17, 25 \\
  \colsquare{cstaff}{10pt} & Staff & 16, 20 \\
  \colsquare{cpress}{10pt} & Press & 4 \\
  \colsquare{chill}{10pt} & Hillary & 12 \\
  \colsquare{cmeet}{10pt} & Meetings & 1, 9, 10, 24, 28, 30 \\
  \colsquare{ccomm}{10pt} & Common & 3, 8, 14, 15 \\
  \bottomrule
\end{tabular}
\caption{Topic Categorization}
\label{tab:topic_cat}
\end{table}

\begin{table}[htb] \centering
\setlength{\tabcolsep}{1pt}
\begin{tabular}{cccccccccccccccccccccccccc}
  \toprule
  \colsquare[-3pt]{cforeign}{16pt} &
  \colsquare[-3pt]{cmeet}{16pt} &
  \colsquare[-3pt]{cmeet}{16pt} &
  \colsquare[-3pt]{cmeet}{16pt} &
  \colsquare[-3pt]{cmeet}{16pt} &
  \colsquare[-3pt]{cmeet}{16pt} &
  \colsquare[-3pt]{cpress}{16pt} &
  \colsquare[-3pt]{cmeet}{16pt} &
  \colsquare[-3pt]{cmideast}{16pt} &
  \colsquare[-3pt]{cmideast}{16pt} &
  \colsquare[-3pt]{cstaff}{16pt} &
  \colsquare[-3pt]{chill}{16pt} &
  \colsquare[-3pt]{cstaff}{16pt} &
  \colsquare[-3pt]{cpolitics}{16pt} &
  \colsquare[-3pt]{cforeign}{16pt} &
  \colsquare[-3pt]{cmideast}{16pt} &
  \colsquare[-3pt]{cforeign}{16pt} &
  \colsquare[-3pt]{cmideast}{16pt} &
  \colsquare[-3pt]{cterror}{16pt} &
  \colsquare[-3pt]{cmideast}{16pt} &
  \colsquare[-3pt]{cforeign}{16pt} &
  \colsquare[-3pt]{cpolitics}{16pt} &
  \colsquare[-3pt]{cforeign}{16pt} &
  \colsquare[-3pt]{cforeign}{16pt} &
  \colsquare[-3pt]{cpolitics}{16pt} &
  \colsquare[-3pt]{cterror}{16pt} \\
  21 & 1 & 28 & 30 & 10 & 9 & 4 & 24 & 18 & 29 & 16 & 12 & 20 &
  17 & 13 & 19 & 23 & 27 & 22 & 6 & 2 & 25 & 26 & 7 & 11 & 5 \\
  \midrule
  \multicolumn{13}{l}{Most Frequent} & \multicolumn{13}{r}{Least Frequent} \\
  \bottomrule
\end{tabular}
\setlength{\tabcolsep}{6pt}
\caption{Primary Topic Frequency}
\label{tab:topic_freq}
\end{table}

@@

\begin{figure}[htb] \centering
  \includegraphics[width=0.95\linewidth]{../images/coefficients.pdf}
  \caption{Normalized coefficients from a multinomial logistic regression of email sender on LDA topic proportions.}
  \label{fig:coefficients}
\end{figure}
